---
title: "daily26"
format:
  html:
    self-contained: true
execute:
  echo: true
---


```{r}
url <- '/vsicurl/https://raw.githubusercontent.com/mikejohnson51/csu-ess-330/refs/heads/main/resources/foco-elev-cm.tif'
rast_obj <- terra::rast(url)

```

## The raster data represents elevation in the Fort Collins area, originally measured in centimeters. It consists of a single-layer raster with regularly spaced grid cells, where each cell holds an elevation value. After reading the raster into R using the terra package, the data shows a continuous numeric distribution with no categorical parts. The structure confirms it's a single-band raster which would work well for spatial analysis and visualization.

```{r}
elev_feet <- rast_obj * 0.0328084

```

```{r}
elev_vals <- terra::values(elev_feet, dataframe = TRUE)

```

```{r}
gg <- ggdensity(elev_vals, x = "dem", 
                fill = "lightblue", 
                title = "Elevation Density (Feet)", 
                xlab = "Elevation (feet)")
print(gg)

```

```{r}
ggsave("elevation_density.png", gg)

```

